ZCB Pricing

### 2018-10-18 ZCB Pricing .Rmd
Comments added

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r # Initial rates on first row.
  z = matrix(nrow=n, ncol=s)
  for (i in 1:n){
    z[i,]=rnorm(s)
  }

@@

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using negative values of RV
  sim_path[1,] = r
  sim_path_inv[1,] = r
  z = matrix(nrow=n, ncol=s)
  for (i in 1:n){
    z[i,]=rnorm(s)
  }
  z.=-z

@@

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r
  z = matrix(nrow=n, ncol=s)
  for (i in 1:n){
    z[i,]=rnorm(s)
  }

  z_m = matrix(nrow=n, ncol=s)
  for (i in 1:n){
    z_m[i,]=z[i,]-mean(z[i,])
  }
  # Moment matching transformation of Z_i to match finite moments

@@

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r
  z = matrix(nrow=n, ncol=s)
  for (i in 1:n){
    z[i,]=rnorm(s)
  }

@@

for ( i in 1:100){
  CR[i]=Crude_Monte_Carlo()

>>>>

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r # Initial rates on first row.
  z = matrix(nrow=n, ncol=s) # Create a matrix of standardised normal random variables
  for (i in 1:n){
    z[i,]=rnorm(s)
  }

@@

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using negative values of RV
  sim_path[1,] = r
  sim_path_inv[1,] = r
  z = matrix(nrow=n, ncol=s)
  for (i in 1:n){
    z[i,]=rnorm(s)# Create a matrix of standardised normal random variables
  }
  z.=-z #Take the negative of above matrix

@@

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r
  z = matrix(nrow=n, ncol=s)
  for (i in 1:n){
    z[i,]=rnorm(s) # Create a matrix of standardised normal random variables
  }

  z_m = matrix(nrow=n, ncol=s)
  for (i in 1:n){
    z_m[i,]=z[i,]-mean(z[i,]) # Perform the moment matching transformation on the                                 above generated random variables
  }
  # Moment matching transformation of Z_i to match finite moments

@@

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r
  z = matrix(nrow=n, ncol=s)
  for (i in 1:n){
    z[i,]=rnorm(s) # Create a matrix of standardised normal random variables
  }

@@

# Determine the price under each method 100 times
for ( i in 1:100){
  CR[i]=Crude_Monte_Carlo()
